\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage[expansion=false]{microtype}
\usepackage{geometry}
\geometry{a4paper, margin=1in}


\name{Victor Guilherme de O.}{Barreto}
\address{Rua Aniceto Arão, Três Lagoas, MS, Brazil, ZIP: 79645-230}{}{}
\phone{+55 67 98133-5413}
\email{victorguilherme.barreto@gmail.com}
\extrainfo{Brazilian | Age: 23 | Gender: Male | Marital Status: Single}

\begin{document}

\makecvtitle

\section{Professional Objective}
I.T. Technical, Aspiring software developer seeking opportunities to launch a professional career in programming. Currently nearing completion of a degree in Systems Analysis and Development, with a strong foundation in computing and a personal passion for electronics and hardware repair. Highly motivated to contribute in roles related to programming and DevOps, where technical aptitude and problem-solving skills can be effectively applied.

\section{Education}
\cventry{2023--Present}{Bachelor of Technology in Systems Analysis and Development}{Federal Institute of Mato Grosso do Sul (IFMS)}{}{}{}
\cventry{2017--2021}{Technical High School in Electrotechnics}{Federal Institute of Mato Grosso do Sul (IFMS)}{}{}{}

\section{Qualifications}
\cvitem{Languages}{Native Brazilian Portuguese, Intermediate English (reading and writing), Basic Japanese}
\cvitem{Operational Systems}{Linux and Windows (Basic Usage, configuration and maintenance)}
\cvitem{Programming Languages}{Python (back-end programming using FastAPI and Flask, automation scripts) Typescript (react-native applications with Expo)}
\cvitem{Other}{Advanced knowledge in IT (hardware and software)}

\section{Extras}
\cvitem{}{Driver License (A and B)}
\cvitem{}{Relocate Availability for Portugal.}


\section{Professional Experience}
\cventry{2023--Present}{IT Technician}{Três Lagoas Comércio de Informática LTDA}{}{}{Responsible for diagnosing and repairing electronic devices including laptops, desktops, and printers. Provide technical support to clients, addressing operational issues and system failures with efficiency and professionalism.}
\cventry{2021--2022}{Receptionist / Administrative Assistant}{Orbenk (Contracted by Federal Highway Police)}{}{}{Performed administrative duties at the Federal Highway Police office, including document processing, public service, and IT support for internal systems and equipment.}
\cventry{2019--2020}{Intern – Administrative Technician}{State Public Prosecutor's Office}{}{}{Engaged in data entry, document preparation, public service, and technical support for IT infrastructure. Assisted in maintaining operational efficiency within the administrative department.}

\end{document}
